High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-18 doc/asplos2013/interface.tex
More work on the interface section

>>>>

The LLR interface uses {\em physical regions} as an abstraction for reasoning about
the placement and movement of data in the memory hierarchy.  Physical regions imply a specific
allocation of data in a single memory in the memory hierarchy.  Listing~\ref{lst:regionapi} 
shows a subset of the physical region interface.  The first object in the interface
is a {\tt RegionMetaData} object (line 1).  {\tt RegionMetaData} objects 
do not actually allocate data, but instead provide an interface for the
creation of physical regions called {\tt RegionInstance} objects (line 17).  {\tt RegionMetaData}
objects are crucial for the movement of data by the runtime.  The runtime is only able
to copy data between two {\tt RegionInstance} objects that were created by the
same {\tt RegionMetaData} object.  A runtime error will be generated if a copy is attempted
between two {\tt RegionInstance} objects that were not created by the same {\tt RegionMetaData}.

When creating a {\tt RegionInstance} object the programmer must specify the {\tt Memory}
in which the instance is going to be allocated (line 10).  Once the {\tt RegionInstance} is created it
cannot be moved.   There is no coherence of data between {\tt RegionInstance} objects of the
same {\tt RegionMetaData}.  It is the programmer's responsiblity to manage data coherence
using copies between {\tt RegionInstance} objects (line 22-23).  Just like other operations
copies can be predicated on an {\tt Event} and return an {\tt Event} corresponding to
completion.  A copy between two {\tt RegionInstance} objects can only be performed if copies
are permitted between their two memories.  A test of whether copies can be performed can be performed 
by a query of the {\tt Machine} object (see Section~\ref{subsec:machmodel}).

\begin{lstlisting}[float={t},label={lst:regionapi},caption={Subset of Physical Region Interface.}]
class RegionMetaData {
public:
  const unsigned id;
  static const RegionMetaData NO_REGION;
  // Create and destroy metadatas
  static RegionMetaData create_region(size_t num_elmts, 
                                      size_t elmt_size);
  void destroy_region() const;
  // Create and destroy instances
  RegionInstance create_instance(Memory memory) const;
  void destroy_instance(RegionInstance instance) const;
  // Create a physical instance only for reductions
  RegionInstance create_instance(Memory memory, 
                        ReductionOpID redopid) const;
};

class RegionInstance {
public:
  const unsigned id;
  static const RegionInstance NO_INST;
  // Copy between instances
  Event copy_to(RegionInstance target, 
                Event wait_on = Event::NO_EVENT);
};
\end{lstlisting}
